My title

### 2024-02-14 paper/paper.qmd
Updated quarto file and comments

The remainder of this paper is structured as follows. In @sec-data, we compile the subset of data that only includes the students that took part in the public treatment study and not the private treatment study, as students were offered more information to inform their final decisions when able to see the incentive status of their peers. In @sec-results, we dive deeper into analyzing possible factors that may influence a student's final food choice in stage G2. We leverage ggplot2 in creating bar graphs to represent the grouped data for the various factors that were analyzed. Finally, in @sec-discussion, we summarize our results and also identify other factors or biases that may have affected the results, on a qualitative or quantitative level.

>>>>

The remainder of this paper is structured as follows. In @sec-data, we compile the subset of data that only includes the students that took part in the public treatment study and not the private treatment study, as students were offered more information to inform their final decisions when able to see the incentive status of their peers. In @sec-results, we dive deeper into analyzing possible factors that may influence a student's final food choice in stage G2. We leverage `ggplot2` in creating bar graphs to represent the grouped data for the various factors that were analyzed. Finally, in @sec-discussion, we summarize our results and also identify other factors or biases that may have affected the results, on a qualitative or quantitative level.

The graphs and tables in this paper were created in R Studio using R [@citeR] and the analysis in a Quarto document. The analysis was conducted with the use of the `ggplot`, `tiddyverse`, `knitr`, `kableExtra`, and `dyplr` packages. The replications of the original graphs and tables were completed with the `semiPar`, `janitor`, `tiddyverse`, `knitr`, and `kableExtra` packages.

Estimand: TBD
